Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
Abstract

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    With these deeper data, we show definitively that at fixed stellar mass,
    massive central galaxies display mass density profiles that are not self similar, 
    with the accreted fraction increasing towards unity for galaxies in our highest 
    stellar mass bin. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.
    \song{First trial by Jenny; need more works}

>>>>

    \update{
    Massive galaxies are important to our understanding of galaxy formation, and 
    their extended stellar halos contain crucial fossil records of their assembly 
    history. 
    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
    survey to investigate the surface mass density profiles and outer stellar halos 
    of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
    miss the extended stellar halo and result in underestimated stellar mass in a 
    mass-dependent way.  
    It will impact important applications like the measurements of the stellar mass 
    function. 
    With these deeper data, we explicitly show that at fixed stellar mass,
    massive central galaxies display surface mass density profiles that are not 
    self-similar, with the outer-slope becoming shallower and the fraction of mass 
    in the outskirt increasing with total stellar mass.
    We also show that the ellipticity of the stellar halo increases with stellar
    mass, while the optical color gradients do not strongly depend on stellar mass.
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretions of small systems. 
    The surface mass density profiles are provided in a convenient tabulated format 
    in order to facilitate comparisons with predictions from numerical simulations 
    of galaxy formation.
    }
